This paper describes a university timetabling system that schedules academic activities on a fixed weekly grid.
The primary goal is feasibility under hard constraints (no conflicts, availability, room eligibility), with secondary quality objectives such as reducing gaps and improving schedule stability across weeks.

Automated timetabling is a mature research area with broad surveys on exact and heuristic methods~\cite{schaerf1999survey,lewis2008metaheuristics}.
Benchmark-driven progress has been shaped by the International Timetabling Competitions and follow-up analyses~\cite{mccollum2010itc,bonutti2012benchmarking,bettinelli2015overview}.

Our contributions are:
\begin{itemize}[leftmargin=*]
  \item A formal start-time assignment model with binary decision variables, occupancy-based non-overlap constraints, and rule constraints for institutional policies.
  \item A hybrid rooming formulation that supports either integrated CP room assignment or a decoupled post-processing assignment, enabling strictness/runtime trade-offs.
  \item A weighted soft-penalty objective and a feasibility-preserving local-search layer that improves timetable quality under bounded time.
  \item A phased anytime solving policy (feasibility phase then improvement phase) with explicit budget partitioning.
  \item A reproducible implementation in OR-Tools CP-SAT with a shared CLI/UI runtime and export pipeline~\cite{cpsatlp,ortools,ortools_cite,perron_didier_gay_cpsatlp_2023}.
\end{itemize}

All non-trivial solver claims in this paper are tied directly to the implementation and/or cited references.
Experimental results are produced by running the released code and are not inferred.
