Automated university timetabling is typically studied through three families of methods: exact/constraint-based optimization, metaheuristics, and hybrids.
Survey work highlights that no single family dominates all instances; performance depends strongly on structure and constraint tightness~\cite{schaerf1999survey,lewis2008metaheuristics,bettinelli2015overview}.

\paragraph{Competition-driven modeling.}
ITC-style benchmark design emphasized clear hard/soft separation, reproducible formats, and comparable scoring~\cite{mccollum2010itc,bonutti2012benchmarking}.
Our formulation follows this pattern directly: hard feasibility first, weighted soft penalties second, with explicit validation and reproducibility artifacts.

\paragraph{Metaheuristics.}
Neighborhood search (tabu, SA, VNS, large-neighborhood variants) is effective for quality improvement after feasibility, especially when incremental delta evaluation is available~\cite{lewis2008metaheuristics}.
The local-search layer in this work follows that direction, but with bounded deterministic passes before stochastic exploration to improve predictability in interactive runs.

\paragraph{Constraint programming and hybrid solvers.}
Competition solvers and later systems often combine exact modeling with heuristic guidance~\cite{muller2009hybrid}.
Modern CP-SAT combines SAT-style propagation, integer reasoning, and linear relaxations in one engine, enabling strong feasibility search under mixed logical/arithmetic constraints~\cite{cpsatlp,ortools,perron_didier_gay_cpsatlp_2023}.
Relative to pure metaheuristics, our system uses CP-SAT to guarantee hard feasibility (when a feasible model is found) and then applies local search only for soft improvement.

\paragraph{Positioning of this paper.}
Methodologically, the contribution is not a new global algorithm class, but an implementation-grounded integration of:
\begin{itemize}[leftmargin=*]
  \item a CP-SAT hard model with explicit occupancy and rule constraints,
  \item switchable strict/greedy rooming to trade strictness for runtime,
  \item bounded post-optimization tuned for interactive administration.
\end{itemize}
This placement is closest to practical hybrid workflows used in deployable timetabling tools, while keeping the mathematical model explicit and reproducible.
