This section presents the scheduling formulation in a standard mixed 0--1 form.
CP-SAT is used as the optimization engine, with interval variables for non-overlap constraints.

\subsection{Time Encoding and Start Variables}
For each week, index time within the week by $t \in \{0,\dots,|\mathcal{D}|S-1\}$ where
$t = \mathrm{dayIndex}(d)\cdot S + s$.

Each activity $a$ has a set of allowed start indices $T_a$ derived from staff availability, duration feasibility, and optional locks.
Introduce binary variables $x_{a,t}\in\{0,1\}$ for $t\in T_a$ indicating that activity $a$ starts at time $t$.
\begin{align}
\sum_{t\in T_a} x_{a,t} &= 1 \qquad \forall a\in\mathcal{A}. \label{eq:oneStart}
\end{align}

\subsection{Interval Non-Overlap Constraints}
Let $\mathrm{Occ}(a,t,\tau)$ be 1 iff slot $\tau$ is covered when activity $a$ starts at $t$, i.e.,
$\tau \in [t, t+\mathrm{dur}(a)-1]$.

\paragraph{Group conflicts.}
For each group $g$, week $w$, and time slot $\tau$:
\begin{align}
\sum_{\substack{a\in\mathcal{A}:\\ g\in\mathcal{G}(a),\,\mathrm{week}(a)=w}}
\;\sum_{t\in T_a:\,\mathrm{Occ}(a,t,\tau)=1} x_{a,t} \;\le\; 1.
\end{align}

\paragraph{Staff conflicts.}
Analogously, for each staff member $p$, week $w$, and time slot $\tau$:
\begin{align}
\sum_{\substack{a\in\mathcal{A}:\\ \mathrm{staff}(a)=p,\,\mathrm{week}(a)=w}}
\;\sum_{t\in T_a:\,\mathrm{Occ}(a,t,\tau)=1} x_{a,t} \;\le\; 1.
\end{align}

The implementation uses CP-SAT interval variables and \texttt{AddNoOverlap} for these constraints.

\subsection{Rule Constraints}
\paragraph{Week-1 lectures-only.}
If $w_0=\min(\mathcal{W})$, then activities of kind TUT/LAB are forbidden in week $w_0$.
The implementation rejects such instances during model construction.

\paragraph{Load caps (optional).}
If $\mathrm{MaxWeek}(p)$ is specified, enforce:
\begin{align}
\sum_{\substack{a:\,\mathrm{staff}(a)=p,\,\mathrm{week}(a)=w}} \mathrm{dur}(a) \le \mathrm{MaxWeek}(p) \qquad \forall p,w.
\end{align}
Similarly, if $\mathrm{MaxDay}(p)$ is specified, enforce per-day caps.

\paragraph{Block-only professors.}
For staff with a \emph{block-only} flag, lectures for a given course in a given week must form a single contiguous block of length 2--3 on one day.
The implementation encodes this via per-slot occupancy indicators and a ``single block-start'' constraint.

\subsection{Clustering (Co-Location)}
Certain activity sets are designated as clusters (e.g., shared lectures across groups, cross-major clusters).
For each cluster $C$ with leader $\ell$, enforce equal start times:
\begin{align}
\mathrm{start}(a) = \mathrm{start}(\ell) \qquad \forall a\in C.
\end{align}

\subsection{Soft Objective (Optional)}
When objective mode is enabled, the model minimizes
\begin{align}
\min_{x}\; F(x)
&=
w_{\mathrm{free}}\,P_{\mathrm{free}}(x)
+w_{\mathrm{gap}}\,P_{\mathrm{gap}}(x)
+w_{\mathrm{late}}\,P_{\mathrm{late}}(x)\nonumber\\
&\quad
+w_{\mathrm{stab}}\,P_{\mathrm{stab}}(x)
+w_{\mathrm{room}}\,P_{\mathrm{room}}(x),
\label{eq:softobj}
\end{align}
where each \(P_{\bullet}(x)\) is a nonnegative linearized penalty term:
free-day shortfalls, intra-day gaps, late starts, week-to-week instability, and
room inconsistency (when rooming is integrated in CP).
All weights \(w_{\bullet}\ge 0\) are configurable at the instance level.

If objective mode is disabled, the solver runs in pure feasibility mode:
find any \(x\) satisfying all hard constraints.
