This section reports controlled empirical measurements under fixed seeds and solver budgets.

\subsection{Research Questions}
We evaluate four practical questions:
\begin{itemize}[leftmargin=*]
  \item \textbf{RQ1 (Feasibility reliability):} does the retry/fallback pipeline consistently return a feasible schedule?
  \item \textbf{RQ2 (Runtime trade-off):} how much faster is requested \texttt{greedy} room mode than requested \texttt{cp\_rooms} on larger scenarios?
  \item \textbf{RQ3 (Fallback behavior):} how often do strict-room requests end up requiring greedy fallback?
  \item \textbf{RQ4 (Quality improvement):} how much penalty reduction is obtained by local-search post-improvement?
\end{itemize}

\subsection{Setup}
All runs are produced by the batch driver script \texttt{run\_experiment\_batches.sh}.
We evaluate modes \texttt{small\_demo}, \texttt{block\_profs}, \texttt{mixed\_large}, and \texttt{target\_case}
with seeds \(\{1,2,3\}\).

\paragraph{Batch A reliability/runtime}
\begin{itemize}[leftmargin=*]
  \item requested room modes: \(\{\texttt{cp\_rooms}, \texttt{greedy}\}\),
  \item objective on first attempt, objective-off retry enabled,
  \item \texttt{cp\_rooms} \(\rightarrow\) \texttt{greedy} fallback enabled,
  \item strict first-attempt budget: \(20\) s,
  \item per-attempt time limit: \(60\) s,
  \item workers: \(4\),
  \item local search disabled (\texttt{ls\_iters}=0).
\end{itemize}
This produces 24 runs in total.

\paragraph{Batch B local-search ablation}
\begin{itemize}[leftmargin=*]
  \item requested room mode: \texttt{greedy},
  \item same retry/fallback and CP limits as Batch A,
  \item local search enabled with \texttt{ls\_iters}=150 and \texttt{ls\_seconds}=8,
  \item deterministic group/week pre-pass enabled (worst groups first) with bounded compound lookahead,
  \item guided stochastic neighborhood search with bounded restart/diversification defaults,
  \item entity-priority targeting enabled (worst groups/staff are optimized first).
\end{itemize}
This produces 12 runs in total and is used for RQ4.

The JSONL outputs are then aggregated into LaTeX table rows.

\subsection{Results}
\paragraph{RQ1 (Feasibility reliability).}
All 24/24 Batch-A runs are feasible (100\%).

\paragraph{RQ2 (Runtime trade-off).}
Table~\ref{tab:perf} and Figure~\ref{fig:runtime_compare} show that on larger scenarios, requested \texttt{greedy} is consistently faster:
\begin{itemize}[leftmargin=*]
  \item \texttt{block\_profs}: \(87.48\) s (\texttt{cp\_rooms}) vs \(47.59\) s (\texttt{greedy}), \(\approx 1.84\times\),
  \item \texttt{mixed\_large}: \(103.28\) s vs \(65.12\) s, \(\approx 1.59\times\),
  \item \texttt{target\_case}: \(98.34\) s vs \(49.59\) s, \(\approx 1.98\times\).
\end{itemize}
For \texttt{small\_demo}, both requested modes are effectively identical (\(20.17\) s vs \(20.03\) s).

\paragraph{RQ3 (Fallback behavior).}
Among 12 runs that request \texttt{cp\_rooms}, only 3 finish in \texttt{cp\_rooms}
(all \texttt{small\_demo}); the remaining 9 finish via \texttt{greedy} fallback
(Figure~\ref{fig:fallback_outcomes}).
This confirms that integrated strict rooming is the main bottleneck under short strict budgets.

\paragraph{RQ4 (Quality improvement).}
Table~\ref{tab:ls} and Figure~\ref{fig:ls_gain} summarize base-vs-LS penalties for Batch B.
Local search always preserves or improves penalty in this batch:
\begin{itemize}[leftmargin=*]
  \item \texttt{block\_profs}: median \(-149\) penalty points (\(1.13\%\)),
  \item \texttt{mixed\_large}: median \(-34\) (\(0.26\%\)),
  \item \texttt{target\_case}: median \(-58\) (\(0.50\%\)),
  \item \texttt{small\_demo}: median change \(0\).
\end{itemize}

\paragraph{Retry dynamics (additional evidence).}
Objective-off retries are never needed for \texttt{small\_demo} (0/6 runs),
but are needed in all large-scenario runs in this batch (3/3 per requested mode for
\texttt{block\_profs}, \texttt{mixed\_large}, and \texttt{target\_case}; see Table~\ref{tab:perf}).
This supports the design choice of retaining an automatic objective-off retry path.

\subsection{External Benchmark Positioning}
This submission reports claims on the project's generated workloads only.
For broader cross-paper score comparison, public benchmark ingestion and schema mapping (e.g., ITC-style CB-CTT datasets)
remain future work~\cite{itc2007_track3,mccollum2010itc,bonutti2012benchmarking,bettinelli2015overview}.

\subsection{Tables}
Detailed per-run results are provided as supplementary table rows in \texttt{sections/07\_experiments\_runs.tex}.

\subsection{Comparison Diagrams}
\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=5.2pt,
    width=0.96\columnwidth,
    height=0.52\columnwidth,
    ymin=0,
    ylabel={Median runtime (s)},
    symbolic x coords={SD,BP,ML,TC},
    xtick=data,
    enlarge x limits=0.18,
    legend style={at={(0.5,1.02)},anchor=south,legend columns=2,font=\footnotesize},
    tick label style={font=\scriptsize},
    label style={font=\footnotesize},
]
\addplot coordinates {(SD,20.17) (BP,87.48) (ML,103.28) (TC,98.34)};
\addplot coordinates {(SD,20.03) (BP,47.59) (ML,65.12) (TC,49.59)};
\legend{Requested \texttt{cp\_rooms}, Requested \texttt{greedy}}
\end{axis}
\end{tikzpicture}
\caption{Runtime comparison for requested room modes (Batch A medians; SD=\texttt{small\_demo}, BP=\texttt{block\_profs}, ML=\texttt{mixed\_large}, TC=\texttt{target\_case}).}\label{fig:runtime_compare}
\end{figure}

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=16pt,
    width=0.88\columnwidth,
    height=0.48\columnwidth,
    ymin=0,
    ymax=12,
    ylabel={Run count},
    symbolic x coords={CPReq},
    xtick=data,
    xticklabels={Requested \texttt{cp\_rooms}},
    enlarge x limits=0.35,
    legend style={at={(0.5,1.02)},anchor=south,legend columns=2,font=\footnotesize},
    nodes near coords,
    nodes near coords align={vertical},
    every node near coord/.append style={font=\scriptsize},
    tick label style={font=\scriptsize},
    label style={font=\footnotesize},
]
\addplot coordinates {(CPReq,3)};
\addplot coordinates {(CPReq,9)};
\legend{Final \texttt{cp\_rooms}, Final \texttt{greedy} (fallback)}
\end{axis}
\end{tikzpicture}
\caption{Fallback outcomes when strict room mode is requested (12 runs total).}\label{fig:fallback_outcomes}
\end{figure}

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=8pt,
    width=0.96\columnwidth,
    height=0.48\columnwidth,
    ymin=0,
    ylabel={Median LS gain (\%)},
    symbolic x coords={SD,BP,ML,TC},
    xtick=data,
    enlarge x limits=0.22,
    nodes near coords,
    nodes near coords align={vertical},
    every node near coord/.append style={font=\scriptsize},
    tick label style={font=\scriptsize},
    label style={font=\footnotesize},
]
\addplot coordinates {(SD,0.00) (BP,1.13) (ML,0.26) (TC,0.50)};
\end{axis}
\end{tikzpicture}
\caption{Median local-search improvement over base penalty (Batch B).}\label{fig:ls_gain}
\end{figure}

\begin{table*}[t]
\centering
\footnotesize
\setlength{\tabcolsep}{5pt}
\begin{tabular}{lrrrrrrr}
\toprule
Scenario & Req.\ mode & Runs & Feasible (\%) & Median CP (s) & Median base penalty & Median LS penalty & Objective retries \\
\midrule
block\_profs & cp\_rooms & 3 & 100.00 & 87.48 & 13220.00 & - & 3 \\
block\_profs & greedy & 3 & 100.00 & 47.59 & 13220.00 & - & 3 \\
mixed\_large & cp\_rooms & 3 & 100.00 & 103.28 & 12920.00 & - & 3 \\
mixed\_large & greedy & 3 & 100.00 & 65.12 & 12920.00 & - & 3 \\
small\_demo & cp\_rooms & 3 & 100.00 & 20.17 & 55.00 & - & 0 \\
small\_demo & greedy & 3 & 100.00 & 20.03 & 46.00 & - & 0 \\
target\_case & cp\_rooms & 3 & 100.00 & 98.34 & 11691.00 & - & 3 \\
target\_case & greedy & 3 & 100.00 & 49.59 & 11691.00 & - & 3 \\
\bottomrule
\end{tabular}
\caption{Aggregated reliability/runtime metrics (Batch A).}\label{tab:perf}
\end{table*}

\begin{table*}[t]
\centering
\footnotesize
\setlength{\tabcolsep}{5pt}
\begin{tabular}{lrrrrr}
\toprule
Scenario & Runs & Median base penalty & Median LS penalty & Median delta & Median improvement (\%) \\
\midrule
block\_profs & 3 & 13220.00 & 13071.00 & 149.00 & 1.13 \\
mixed\_large & 3 & 12920.00 & 12886.00 & 34.00 & 0.26 \\
small\_demo & 3 & 49.00 & 49.00 & 0.00 & 0.00 \\
target\_case & 3 & 11691.00 & 11633.00 & 58.00 & 0.50 \\
\bottomrule
\end{tabular}
\caption{Local-search ablation metrics (Batch B).}\label{tab:ls}
\end{table*}
