This section reports measurements from running the released code and scripts.

\subsection{Research Questions}
We evaluate four practical questions:
\begin{itemize}[leftmargin=*]
  \item \textbf{RQ1 (Feasibility reliability):} does the retry/fallback pipeline consistently return a feasible schedule?
  \item \textbf{RQ2 (Runtime trade-off):} how much faster is requested \texttt{greedy} room mode than requested \texttt{cp\_rooms} on larger scenarios?
  \item \textbf{RQ3 (Fallback behavior):} how often do strict-room requests end up requiring greedy fallback?
  \item \textbf{RQ4 (Quality improvement):} how much penalty reduction is obtained by local-search post-improvement?
\end{itemize}

\subsection{Setup}
All runs are produced by \texttt{scripts/run\_experiment\_batches.sh}.
We evaluate modes \texttt{small\_demo}, \texttt{block\_profs}, \texttt{mixed\_large}, and \texttt{target\_case}
with seeds \(\{1,2,3\}\).

\paragraph{Batch A: reliability/runtime.}
\begin{itemize}[leftmargin=*]
  \item requested room modes: \(\{\texttt{cp\_rooms}, \texttt{greedy}\}\),
  \item objective on first attempt, objective-off retry enabled,
  \item \texttt{cp\_rooms} \(\rightarrow\) \texttt{greedy} fallback enabled,
  \item strict first-attempt budget: \(20\) s,
  \item per-attempt time limit: \(60\) s,
  \item workers: \(4\),
  \item local search disabled (\texttt{ls\_iters}=0).
\end{itemize}
This produces 24 runs in total.

\paragraph{Batch B: local-search ablation.}
\begin{itemize}[leftmargin=*]
  \item requested room mode: \texttt{greedy},
  \item same retry/fallback and CP limits as Batch A,
  \item local search enabled with \texttt{ls\_iters}=150 and \texttt{ls\_seconds}=8.
\end{itemize}
This produces 12 runs in total and is used for RQ4.

The JSONL outputs are converted to LaTeX rows by:
\texttt{scripts/jsonl\_to\_latex\_table.py} and \texttt{scripts/jsonl\_to\_latex\_ls\_table.py}.

\subsection{Results}
\paragraph{RQ1 (Feasibility reliability).}
All 24/24 Batch-A runs are feasible (100\%).

\paragraph{RQ2 (Runtime trade-off).}
Table~\ref{tab:perf} shows that on larger scenarios, requested \texttt{greedy} is consistently faster:
\begin{itemize}[leftmargin=*]
  \item \texttt{block\_profs}: \(87.48\) s (\texttt{cp\_rooms}) vs \(47.59\) s (\texttt{greedy}), \(\approx 1.84\times\),
  \item \texttt{mixed\_large}: \(103.28\) s vs \(65.12\) s, \(\approx 1.59\times\),
  \item \texttt{target\_case}: \(98.34\) s vs \(49.59\) s, \(\approx 1.98\times\).
\end{itemize}
For \texttt{small\_demo}, both requested modes are effectively identical (\(20.17\) s vs \(20.03\) s).

\paragraph{RQ3 (Fallback behavior).}
Among 12 runs that request \texttt{cp\_rooms}, only 3 finish in \texttt{cp\_rooms}
(all \texttt{small\_demo}); the remaining 9 finish via \texttt{greedy} fallback.
This confirms that integrated strict rooming is the main bottleneck under short strict budgets.

\paragraph{RQ4 (Quality improvement).}
Table~\ref{tab:ls} summarizes base-vs-LS penalties for Batch B.
Local search always preserves or improves penalty in this batch:
\begin{itemize}[leftmargin=*]
  \item \texttt{block\_profs}: median \(-149\) penalty points (\(1.13\%\)),
  \item \texttt{mixed\_large}: median \(-34\) (\(0.26\%\)),
  \item \texttt{target\_case}: median \(-58\) (\(0.50\%\)),
  \item \texttt{small\_demo}: median change \(0\).
\end{itemize}

\subsection{External Benchmark Positioning}
This submission reports claims on the project's generated workloads only.
For broader cross-paper score comparison, public benchmark ingestion and schema mapping (e.g., ITC-style CB-CTT datasets)
remain future work~\cite{itc2007_track3,mccollum2010itc,bonutti2012benchmarking,bettinelli2015overview}.

\subsection{Tables}
The full per-run rows are included in \texttt{sections/07\_experiments\_runs.tex}.

\begin{table}[h]
\centering
\small
\begin{tabular}{lrrrrrrr}
\toprule
Scenario & Req. mode & Runs & Feasible (\%) & Median CP (s) & Median base penalty & Median LS penalty & Objective retries \\
\midrule
\input{sections/07_experiments_table.tex}
\bottomrule
\end{tabular}
\caption{Aggregated reliability/runtime metrics (Batch A).}
\label{tab:perf}
\end{table}

\begin{table}[h]
\centering
\small
\begin{tabular}{lrrrrr}
\toprule
Scenario & Runs & Median base penalty & Median LS penalty & Median delta & Median improvement (\%) \\
\midrule
\input{sections/07_experiments_ls_table.tex}
\bottomrule
\end{tabular}
\caption{Local-search ablation metrics (Batch B).}
\label{tab:ls}
\end{table}
